|

### 2024-10-28 output/seminar-slideshow.qmd
Add labels to IRS contour plot

library(tibble)
library(dplyr)
library(knitr)
library(lavaan)
library(semPlot)
library(extrafont)
library(tidyr)
library(ggplot2)
library(units)
library(ggtext)
library(ggridges)
library(qgraph)
library(purrr)
library(plotly)
```

@@

::: column
```{r mirt-model-irs-3d}
#| fig-width:  5
#| fig-height: 5

mirt_item_probs |>
  ggplot(mapping = aes(trait_1, trait_2, z = prob)) +
  geom_contour() +
  scale_x_continuous(
    minor_breaks = NULL,
    limits = range(PROB_AXIS_2D),
    expand = expansion()
  ) +
  scale_y_continuous(
    minor_breaks = NULL,
    limits = range(PROB_AXIS_2D),
    expand = expansion()
  ) +
  coord_fixed() +
  labs(x = "*&theta;*~1~", y = "*&theta;*~2~") +
  theme(
    axis.title       = element_markdown(),
    axis.title.y     = element_markdown(angle = 90),
    panel.grid.major = element_line(linetype = "17"),
  )

```
:::
:::

>>>>

library(tibble)
library(dplyr)
library(knitr)
library(lavaan)
library(semPlot)
library(extrafont)
library(tidyr)
library(ggplot2)
library(units)
library(ggtext)
library(ggridges)
library(qgraph)
library(purrr)
library(plotly)
library(metR)
```

@@

::: column
```{r mirt-model-irs-contour}
mirt_item_probs |>
  ggplot(mapping = aes(trait_1, trait_2, z = prob, label = after_stat(level))) +
  geom_contour2(
    color = F1_COLOR,
    linewidth = LINE_WIDTH,
    breaks = c(.05, .1, .2, .3, .5, .7, .8, .9, .95),
    label.placer = label_placer_fraction(frac = .18, rot_adjuster = 0)
  ) +
  scale_x_continuous(
    minor_breaks = NULL,
    limits = range(PROB_AXIS_2D),
    expand = expansion()
  ) +
  scale_y_continuous(
    minor_breaks = NULL,
    limits = range(PROB_AXIS_2D),
    expand = expansion()
  ) +
  coord_fixed() +
  labs(x = "*&theta;*~1~", y = "*&theta;*~2~") +
  theme(
    axis.title       = element_markdown(),
    axis.title.y     = element_markdown(angle = 90),
    panel.grid.major = element_line(linetype = "17"),
  )
```
:::
:::
